---
title: "Creating Data Products Final Project: Pitch"
author: "Joakim Kalvenes"
date: "February 14, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Regression model with user-controlled regressors {.smaller}

We have created a [shiny app](https://kalvenes.shinyapps.io/CreatingDataProductsFinalProject/)
that allows users to select which independent variables to include in their regression model
for fuel efficiency (MPG) as a function of car attributes. The data are sourced from the
Motor Trend data set that is included in the standard R distribution. A short description of
the data can be found at the
[ETH Zurich website](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html).

Our app has the following features:

- User selection of regressors using check boxes
- Baseline comparison against our best model (ANOVA)
- Plot of residuals of user model and baseline model
- Display of user model regression coefficients, residuals, and p-values

## Baseline model {.smaller}

```{r}
data("mtcars")
baseFit <- lm(mpg~factor(am)+wt+qsec,data=mtcars)
summary(baseFit)
```

## Residual plot for baseline model  {.smaller}

```{r}
plot(baseFit, which=c(1:1), title("Residual Plot of Base Model"))
```

## Analysis of variance (ANOVA) between baseline and all-in models {.smaller}

The ANOVA results allow the user to evaluate the performance of the custom model
relative to the baseline model. In this example, we have created a custom model
that includes all of the independent variables in the data set. The baseline
model is clearly better than the all-in model.

```{r}
allInFit <- lm(mpg~cyl+disp+hp+drat+wt+qsec+factor(vs)+factor(am)+gear+carb,data=mtcars)
anova(baseFit,allInFit)
```
